Poseidon Adventure

### 2019-05-23 FullSardineTruthEx.Rmd

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'knitr', 'rmarkdown', 'tidyr', 'dplyr', 'ggplot2',
  'data.table', 'here', 'ggforce', 'ggthemes'
), 'packages.bib')
```

@@

On this page we demonstrate use of atlantisom on the California Current output files to provide inputs for a stock assessment model implemented in Stock Synthesis [insert SSREF].

@@

The following settings should achieve a survey that samples all Atlantis model output timesteps, all species, and all model polygons, with perfect efficiency and full selectivity for all ages:

@@

@@

Because we don't want to wait 24 hours for this, we will look at only our three speces and the first 112 time steps.

@@

# get survey nums with full (no) selectivity
catch_testNss <- create_fishery_subset(dat = truth$catch,
                                 time = c(0:111),
                                 species = spp.name,
                                 boxes = boxall)

@@

# aggregate true resn per survey or fishery subset design
catch_aggresnss <- aggregateDensityData(dat = truth$resn,
                                 time = c(0:111),
                                 species = spp.name,
                                 boxes = boxall)

# aggregate true structn per survey or fishery subsetdesign
catch_aggstructnss <- aggregateDensityData(dat = truth$structn,
                                 time = c(0:111),
                                 species = spp.name,
                                 boxes = boxall)

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'knitr', 'rmarkdown', 'tidyr', 'dplyr', 'ggplot2',
  'data.table', 'here', 'ggforce', 'ggthemes', 'r4ss'
), 'packages.bib')
```

@@

On this page we demonstrate use of atlantisom on the California Current output files to provide (true) inputs for a stock assessment model implemented in [Stock Synthesis](https://www.sciencedirect.com/science/article/abs/pii/S0165783612003293). Translation of atlantisom outputs to stock synthesis inputs uses the package [r4ss](https://github.com/r4ss) [@R-r4ss] as demonstrated [here](https://sgaichas.github.io/poseidon-dev/CreateStockSynthesis.html).

@@

@@

Output timesteps and the duration of the model run can be found in the run parameter file [scenario]_run.xml which is read in with `atlantisom::load_runprm`. This is already run in our census_spec.R file. Output timestep toutinc is `r runpar$toutinc `, so steps per year is `r stepperyr ` and the number of output steps is `r noutsteps `.

The settings in `config/census_spec.R` should achieve a survey that samples all Atlantis model output timesteps, all species, and all model polygons, with perfect efficiency and full selectivity for all ages:

@@

Timesteps may be different for fishery output than for the population above. The run parameter file will tell us what time units we are dealing with, and this is already specified in the census_spec.R file as fstepperyr: `r fstepperyr `. Further, we can get the total number of years with nyears from the run parameter file: `r runpar$nyears `.

Now we know the fishery output is annual (365 days), and there will only be 100 years. Because we don't want to wait 24 hours for this, we will look at only our three species.

@@

# get survey nums with full (no) selectivity
catch_testNss <- create_fishery_subset(dat = truth$catch,
                                 time = timeall,
                                 species = spp.name,
                                 boxes = boxall)

@@

# aggregate true resn per survey or fishery subset design
catch_aggresnss <- aggregateDensityData(dat = truth$resn,
                                 time = timeall,
                                 species = spp.name,
                                 boxes = boxall)

# aggregate true structn per survey or fishery subsetdesign
catch_aggstructnss <- aggregateDensityData(dat = truth$structn,
                                 time = timeall,
                                 species = spp.name,
                                 boxes = boxall)

### 2019-05-23 docs/index.Rmd

<a href="https://sgaichas.github.io/poseidon-dev/FullSardineTruthEx.html" target="_blank">Sardines in the CalCurrent, all true data, May 22, 2019</a>

>>>>

<a href="https://sgaichas.github.io/poseidon-dev/FullSardineTruthEx.html" target="_blank">Sardines in the CalCurrent, all true data, May 22, 2019, updated May 23, 2019</a>
